Women work education happiness lol

### 2023-03-15 outputs/paper/paper.qmd
fixed error
Added Appendix material

# Introduction
text goes here

@@

## Data Source and Methodology
text goes here

## Attributes
text goes here

## Analysis
text goes here

### Mean Education Level from 2000 - 2021
```{r}
#| label: fig-1
#| fig-cap: caption goes here
#| echo: false
#| warning: false

@@

merged_gss |> group_by(Year) |> summarize(mean= mean(Highest_Educ_Level, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Mean highest education level of Women over 20 Years",
    x = "Year",
    y = "Mean Educ Level %"
  ) 
```
text goes here

### Mean Occupational Prestige from 2000 - 2021
```{r}
#| label: fig-2
#| fig-cap: caption goes here
#| echo: false
#| warning: false

@@

merged_gss |> group_by(Year) |> summarize(mean = mean(Occupational_Prestige_Pct, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Occupational Prestige of Women over 20 Years",
    x = "Year",
    y = "Mean Occ. Prest. %"
  ) 
```
text goes here

### Women's Happiness from 2000 - 2021
```{r}
#| label: fig-1
#| fig-cap: caption goes here
#| echo: false
#| warning: false

merged_gss |> group_by(Year) |> count(Happiness) |>
  ggplot(aes(x = Year, y = n, fill = Happiness)) +
  geom_col(position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Womens Happiness over 20 Years",
    x = "Year",
    y = "Count"
  )
```
text goes here

# Results
sum up all 3 graphs here

@@

## Womens Education Discussion
jenny section

## Womens Occupational Prestige Discussion
joyce section

## Womens Happiness Discussion
jason section

## Biases and Ethical Concerns
jason

## Weaknesses and next steps
joyce

@@

# Appendix {-}

our survey is here lol

>>>>

# Introduction

text goes here

@@

## Data Source and Methodology

text goes here

## Attributes

text goes here

## Terminology

## Analysis

text goes here

### Mean Education Level from 2000 - 2021

```{r}
#| label: fig-1
#| fig-cap: caption goes here
#| echo: false
#| warning: false

@@

merged_gss |> group_by(Year) |> summarize(mean= mean(Highest_Educ_Level, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Mean highest education level of Women over 20 Years",
    x = "Year",
    y = "Mean Educ Level %"
  ) 
```

text goes here

### Mean Occupational Prestige from 2000 - 2021

```{r}
#| label: fig-2
#| fig-cap: caption goes here
#| echo: false
#| warning: false

@@

merged_gss |> group_by(Year) |> summarize(mean = mean(Occupational_Prestige_Pct, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Occupational Prestige of Women over 20 Years",
    x = "Year",
    y = "Mean Occ. Prest. %"
  ) 
```

text goes here

### Women's Happiness from 2000 - 2021

```{r}
#| label: fig-3
#| fig-cap: caption goes here
#| echo: false
#| warning: false

merged_gss |> group_by(Year) |> count(Happiness) |>
  ggplot(aes(x = Year, y = n, fill = Happiness)) +
  geom_col(position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Womens Happiness over 20 Years",
    x = "Year",
    y = "Count"
  )
```

text goes here

# Results

sum up all 3 graphs here

@@

## Womens Education Discussion

jenny section

## Womens Occupational Prestige Discussion

joyce section

## Womens Happiness Discussion

jason section

## Biases and Ethical Concerns

jason

## Weaknesses and next steps

joyce

@@

# Appendix {.unnumbered}

A link to our survey further exploring the relationship between happiness, occupational prestige level and education level can be found here: <https://forms.gle/iwFwnvGxsiewoKm46>

![SurveyP1](survey1.png)
![SurveyP2](survey2.png)
![SurveyP3](survey3.png)
![SurveyP4](survey4.png)
![SurveyP5](survey5.png)
![SurveyP6](survey6.png)
![SurveyP7](survey7.png)
![SurveyP8](survey8.png)
